\Large Clustering Vehicle Trips Identified from Automatic \\ Number Plate Recognition Camera Scans

### 2018-01-31 paper.tex
Added figures and text to section about data - unfinished
Finished section about ANPR data
Changed title and added bibliography
Fixed affiliation, added biliography and package

\documentclass[twoside,leqno,twocolumn]{article}
\usepackage{ltexpprt}
\usepackage{parskip}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage[many]{tcolorbox}
\usepackage{graphicx}

@@

@@

\title{\Large Classifying Vehicles From Automatic Number \\ Plate Recognition Camera Scans}
\author{Pedro M. Pinto Silva \thanks{School of Computing Science, Newcastle University, United Kingdom}
\and
Matthew Forshaw\footnotemark[1]
\and
Stephen McGough\footnotemark[1]}
\date{}

@@

@@

>>>>

\documentclass[twoside,leqno,twocolumn]{article}
\usepackage{ltexpprt}
\usepackage{parskip}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage[many]{tcolorbox}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{makecell}
\usepackage{float}
\usepackage{placeins}

@@

\graphicspath{{./images/}}

@@

\title{\Large Clustering Vehicle Trips Identified from Automatic \\ Number Plate Recognition Camera Scans}
\author{Pedro M. Pinto Silva \thanks{School of Computing, Newcastle University, United Kingdom}
\and
Matthew Forshaw\footnotemark[1]
\and
Stephen McGough\footnotemark[1]}
\date{}

@@

\bibitem{Clustering}
Chen, Huiyu, Chao Yang, and Xiangdong Xu. {\em Clustering Vehicle Temporal and Spatial Travel Behavior Using License Plate Recognition Data}. Journal of Advanced Transportation 2017 (2017).

@@

\bibitem{Kmeans}
Steinley, Douglas, and Michael J. Brusco. {\em Choosing the number of clusters in Κ-means clustering}. Psychological Methods 16.3 (2011): 285.
